%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    
    \resumeProjectHeading
    {\textbf{Didomi - Cryptocurrency Crowdfunding Platform} $|$ \emph{Next.js, React.js, Nest.js, PostgreSQL, Prisma, Rust, Anchor, Solana}}    {}
    \resumeItemListStart
        \resumeItem {Developed a comprehensive Cryptocurrency Crowdfunding Platform from scratch, utilizing Next.js, React, Nest.js, Prisma, and PostgreSQL for front-end and back-end.}
        \resumeItem{Integrated blockchain functionality by deploying a secure smart contract on Solana using Anchor and Rust, seamlessly connecting front-end, back-end, and on-chain components.}
        \resumeItem{Facilitated seamless cryptocurrency transactions and crowdfunding operations through full-stack development, blockchain integration, and end-to-end project management.}
        \resumeItem{Implemented responsive design principles and modern UI/UX practices to ensure an optimal, intuitive, and visually appealing user experience across a wide range of devices, resulting in a seamless and consistent platform for crowdfunding contributors.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Muve - Playlist Converter} $|$ \emph{ReactJS, Redux, Django, REST API, Tailwind, MUI, Docker, AWS}}    {}
    \resumeItemListStart
        \resumeItem {Developed a Playlist Converter application that seamlessly integrates with YouTube and Spotify APIs, enabling users to effortlessly convert playlists between the two platforms.}
        \resumeItem {Utilized Next.js, React.js for the front-end interface, and Python with Django for the back-end server, ensuring a robust and scalable solution, and implemented responsive design principles to ensure an optimal user experience across various devices.}
        \resumeItem{Demonstrated proficiency in full-stack development, API integration, and handling complex data operations. The application's intuitive interface and seamless playlist conversion functionality got positive feedback from users.}
    \resumeItemListEnd

\resumeSubHeadingListEnd